---
title: "Lac Télé peat swamp forest loss screening: reviewer revision workflow"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
```

# Purpose

This R Markdown file documents the reviewer-revision workflow. The recommended executable workflow is the split script workflow in `00_run_all.R` and the `R/` folder.

# Run complete workflow

```{r run-workflow, eval=FALSE}
source("../00_run_all.R")
```

# Manual validation

The workflow creates:

```text
outputs/reviewer_revision/validation_points_stratified_labeling_template.csv
```

After visual interpretation in Google Earth, Sentinel-2, Planet/NICFI, or another independent reference source, fill `reference_class_binary` with either:

```text
reference_loss_on_peat
reference_not_loss_on_peat
```

Save as:

```text
outputs/reviewer_revision/validation_points_stratified_labelled.csv
```

Then rerun:

```r
source("00_run_all.R")
```

# Outputs generated

The workflow writes expanded validation samples, accuracy metrics, area-adjusted estimates, annual loss tables, forest-threshold sensitivity analyses, resampling sensitivity, QA metadata, FAIR documentation, and checksums.
